\documentclass[12pt]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{indentfirst}
\linespread{1.3}

\usepackage[inline]{enumitem}
\setlist[enumerate]{nosep}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{caption}
\usepackage{subcaption}

\usepackage{fontspec}
\setmainfont{Times New Roman}

\usepackage[compact]{titlesec}

\usepackage{etoolbox}
\patchcmd{\thebibliography}
{\settowidth}
{\setlength{\parsep}{0pt}\setlength{\itemsep}{0pt plus 0.1pt}\settowidth}
{}{}

\usepackage{hyperref}
\urlstyle{same}

\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{listings}
\usepackage{xcolor}
\definecolor{codegreen}{rgb}{0, 0.6, 0}
\definecolor{codegray}{rgb}{0.5, 0.5, 0.5}
\definecolor{codepurple}{rgb}{0.58, 0, 0.82}
\definecolor{backcolour}{rgb}{0.95, 0.95, 0.92}
\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	keepspaces=true,
	numbers=left,
	numbersep=5pt,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	tabsize=2
}
\lstset{style=mystyle}

\usepackage{subfiles}

\begin{document}

\begin{titlepage}
	\subfile{sections/0_title_page}
\end{titlepage}

\section{Introduction}
\subfile{sections/1_introduction}

\section{Objectives}
\subfile{sections/2_objectives}

\section{Detailed Framework}
\subfile{sections/3_detailed_framework}

\section{Results}
\label{sec:results}
\subfile{sections/4_results}

\section{Future Work/Conclusion}
\subfile{sections/5_future_work_conclusion}

\begin{thebibliography}{20}
	\raggedright
	
	\bibitem{bib:part_of_speech_tagging}
	Part-of-speech tagging. (2020, February 15). Retrieved from \url{https://en.wikipedia.org/wiki/Part-of-speech_tagging}
	
	\bibitem{bib:1s_time_limit}
	World Leaders in Research-Based User Experience. (n.d.). Response Time Limits: Article by Jakob Nielsen. Retrieved from \url{https://www.nngroup.com/articles/response-times-3-important-limits/}
	
	\bibitem{bib:compiled_vs_interpreted}
	freeCodeCamp. (n.d.). Compiled Versus Interpreted Languages. Retrieved from \url{https://guide.freecodecamp.org/computer-science/compiled-versus-interpreted-languages/}
	
	\bibitem{bib:numpy_sampling}
	Random sampling (numpy.random)¶. (n.d.). Retrieved from \url{https://docs.scipy.org/doc/numpy-1.15.0/reference/routines.random.html}
	
	\bibitem{bib:numpy_source_code}
	Numpy. (2020, April 8). numpy/numpy. Retrieved from \url{https://github.com/numpy/numpy}
	
	\bibitem{bib:realloc_cost}
	Why not realloc. (n.d.). Retrieved from \url{http://www.iso-9899.info/wiki/Why_not_realloc}
	
	\bibitem{bib:trie_efficiency}
	Trie: (Insert and Search). (2019, September 4). Retrieved from \url{https://www.geeksforgeeks.org/trie-insert-and-search/}
	
	\bibitem{bib:edit_distance}
	Levenshtein distance. (2020, April 7). Retrieved from \url{https://en.wikipedia.org/wiki/Levenshtein_distance}
	
	\bibitem{bib:levenshtein_automaton}
	Levenshtein automata can be simple and fast. (n.d.). Retrieved from \url{http://julesjacobs.github.io/2015/06/17/disqus-levenshtein-simple-and-fast.html}
	
	\bibitem{bib:context_free_grammar}
	Formal Grammars of English. (n.d.). In \textit{Speech and Language Processing: An Introduction to Speech Recognition}. Retrieved from \url{https://cs.pomona.edu/~kim/CSC181S08/text/12.pdf}
	
	\bibitem{bib:regular_grammar}
	Buttery, P. (2018). Formal Models of Language: Formal versus Natural Language. Retrieved from \url{https://www.cl.cam.ac.uk/teaching/1718/ForModLang/notes/Formal_vs_Natural_part1.pdf}
	
	\bibitem{bib:recursive_grammar}
	Recursive grammar. (2018, March 21). Retrieved from \url{https://en.wikipedia.org/wiki/Recursive_grammar}
	
	\bibitem{bib:convergence_factor}
	Generating random sentences from a context free grammar. (n.d.). Retrieved from \url{https://eli.thegreenplace.net/2010/01/28/generating-random-sentences-from-a-context-free-grammar}
	
	\bibitem{bib:engsci_press_media}
	EngSci Press Media. (n.d.). Retrieved from \url{https://drive.google.com/drive/folders/1HlUrUqNho2NtZmqC4janL1xukYZtF2lg?usp=sharing}
	
	\bibitem{bib:c_unicode}
	Unicode in C and C : What You Can Do About It Today. (n.d.). Retrieved \url{from https://www.cprogramming.com/tutorial/unicode.html}
	
	\bibitem{bib:wchar_t}
	Wide character. (2019, December 5). Retrieved from \url{https://en.wikipedia.org/wiki/Wide_character}
\end{thebibliography}

\clearpage

\appendix
\subfile{sections/6_appendices}

\end{document}